Computing Exact Restricted Isometry Constants via\\ Mixed Integer Semidefinite Programming

### 2016-03-16 RIP-MISDP-Paper/IEEE_RIP-MISDP.tex
slight reformulation

The solving times in seconds for the left- and right-hand side of the RIP are given in
Table~\ref{lhsRhsTime}. The relaxation~\eqref{Asp07}
is very fast, taking only a few seconds for all instances. The mixed-integer semidefinite program obviously
cannot compete with these solving times, although for band-matrices, the difference is relatively
small. The Lagrangian Relaxation~\eqref{Asp08}, however, takes more time to produce bounds than is needed
by~\eqref{MISDP} to compute exact solutions. This is mainly caused by the fact that~\eqref{Asp08Dual} involves
$n+1$ $n\times n$ matrix variables and SDP-blocks instead of a single one each in~\eqref{MISDP} and~\eqref{Asp07}.
Furthermore, the big difference is also caused by the instances running into the 
memory limit, but even without those, the algorithm still takes slightly longer than~\eqref{MISDP}.

>>>>

The solving times in seconds for the left- and right-hand side of the RIP are given in
Table~\ref{lhsRhsTime}. The relaxation~\eqref{Asp07}
is very fast, taking only a few seconds for all instances. The mixed-integer semidefinite program obviously
cannot compete with these solving times, although for band-matrices, the difference is relatively
small. The Lagrangian Relaxation~\eqref{Asp08}, however, takes more time to produce bounds than is needed
by~\eqref{MISDP} to compute exact solutions. This is mainly caused by the fact that~\eqref{Asp08Dual} involves
$n+1$ matrix variables of dimension $n\times n$ with corresponding SDP-constraints instead of a 
single one each in~\eqref{MISDP} and~\eqref{Asp07}.
Furthermore, the big difference is also caused by the instances running into the 
memory limit, but even without those, the algorithm still takes slightly longer than~\eqref{MISDP}.
